# Results

We begin with an overall analysis and then move to genre analysis. Finally we reach to analysing popular movie in the most popular genre and to see its connection with other movies.


## Overall Trend

From overall perspective, one thing worth noting is that the movielen dataset isn’t affected by the rapid development of internet. From 1997 to 2019,  approximately 1 million rating as assigned to different movies. Another interesting thing is that, when we calculate rating for each year, it appears to be the same at 3.5 all time! Regarding that we only have 25M data sampling from a large dataset, if it’s not caused by sampling, it exposes a fact that “Mean Reversion” may exist in movie rating! 

```{r , echo=FALSE,fig.width=8, fig.height=6}

library(data.table)
library(dplyr)
library(lubridate)
library(ggplot2)
library(tidyr)
library(reshape2)

rate = fread("../ml-25m/ratings.csv")
movie = fread("../ml-25m/movies.csv")


rate = merge(rate, movie, by = c("movieId"), all.x = TRUE)


rate$date = as.POSIXct(rate$timestamp, origin="1970-01-01", tz="GMT")
rate$date = as.Date(rate$date, "GMT")

rate$year = format(rate$date, format = "%Y")
rate = rate %>% filter(year > 1995)
rate_count = rate %>% group_by(year) %>% summarise(count = n(), mean_score = mean(rating))

rate_count$count = rate_count$count/1000000
rate_cnt_gather = gather(rate_count, key = "name", value = "value", -year)

var_name <- c(
  'count'="Rate Number[M/year]",
  "mean_score"="Average Rating[/5]"
)
g = ggplot(rate_cnt_gather) +
  geom_line(aes(x = year, y = value, group = 1)) +
  ggtitle("Rating Trend & Count Trend",) +
  theme_grey(12) +
  theme(legend.title = element_blank(), plot.title=element_text(hjust=0.5)) +
  scale_x_discrete(breaks = seq(1995, 2020, by = 2)) +
    facet_grid(name~., labeller = as_labeller(var_name))
g


```


## Genre Exploration

Given that we already have a concept for overall data, let's move to the next level. We can divide all the data into different genre and see what kind of genres gets more rating, indicating that more people would like to watch movie under these genres! The figure shown below shows that people love to watch movies related to Drama, Comedy, Action, Thriller and etc...It tells a common sense that most people love to watch something may entertain themselves.


```{r , echo=FALSE, fig.width=8, fig.height=4}

genres = rate %>% select(c("genres", "year", "rating")) %>% 
   mutate(genres =  strsplit(genres, split='|', fixed=TRUE)) %>%
   unnest(c(genres))
genres_cnt = genres %>% group_by(genres) %>% summarise(count = n()/1000000, mean_score = mean(rating)) %>%
  arrange(-count)

ggplot(data=genres_cnt, aes(x=count, y=reorder(genres, count))) +
    geom_bar(stat="identity") + 
  scale_y_discrete("Genre name", expand=c(0,0)) + 
  scale_x_continuous("Total Rating Count[Million]") +
  ggtitle("Rating Count Per Genre",) +
  theme_grey(12) +
  theme(legend.title = element_blank(), plot.title=element_text(hjust=0.5))

rm(genres);invisible(gc())

```


## Popular Genre Trend Analysis

Next, we analysis popular genre trend from year to year, hoping to find some insights from yearly analysis. Interestingly, there's high correlation between these genre. From the figure below, we can find they almost have the same trend over the year!

```{r, echo = FALSE,fig.width=8, fig.height=4}

genres = rate %>% select(c("genres", "year", "rating")) %>% 
   mutate(genres =  strsplit(genres,split='|', fixed=TRUE)) %>%
   unnest(c(genres))

genres_cnt = genres %>% group_by(genres) %>% summarise(count = n(), mean_score = mean(rating)) %>%
  arrange(-count)

top_genres = genres_cnt[1:5, ]
selected_genres = c(top_genres$genres)

genres = genres %>% filter(genres %in% selected_genres)

genres_year = genres %>% group_by(year, genres) %>% summarise(count = n()/1000000, mean_score = mean(rating))

genres_year = genres_year[order(genres_year$genres, genres_year$year),]

ggplot(genres_year,) +
    geom_line( aes(year, count, color = genres, group = genres)) + 
  theme_grey(10) +
  theme(legend.title = element_blank()) +
  scale_x_discrete(breaks = seq(1995, 2020, by = 3)) + 
  ylab("Rating count[Millions]") +
  ggtitle("Rating Count Yearly for Popular Genre",) +
  theme_grey(12) +
  theme(legend.title = element_blank(), plot.title=element_text(hjust=0.5))

  # scale_y_continuous(labels = "Rating count[Millions]")


```

## Overlap for popular genres

The figure above triggers us to think about a question. Since the trend with those genres is so similar, is that some movies contains at least two of them and people love to watch those movies? We categorize movies according to their genre and calculate percentage of each level. We find that 74.8% movies contains at least one of the genre. It tells us that most of films fall into these genres, meaning that people are likely to watch these genres movies. However, it also raises doubt that, is that people love to watch movies from genre, or some movies from these genre attract people to watch and consequently these genres become one of the most popular genre among all the genre?

```{r, echo = FALSE}

for(c in selected_genres){
  movie[,paste(c)] = mapply(grepl, movie$genres, c)
}

movie$cnt = rowSums(movie[,c("Drama","Comedy","Action","Thriller", "Adventure")])


movie$cat = case_when(movie$cnt == 0 ~ "None of popular genre", 
          movie$cnt == 1 ~ "contain 1 famous genre", 
          movie$cnt == 2 ~ "contain 2 famous genre", 
          movie$cnt >= 3 ~ "contain > 3 famous genre", 
          TRUE ~ "NA")

movie_overlap = movie %>% group_by(cat) %>% summarise(count = n())


# Data transformation
movie_overlap <- movie %>% 
  group_by(cat) %>% # Variable to be transformed
  count() %>% 
  ungroup() %>% 
  mutate(perc = `n` / sum(`n`)) %>% 
  arrange(perc) %>%
  mutate(labels = scales::percent(perc))

ggplot(movie_overlap, aes(x = "", y = perc, fill = cat)) +
  geom_col(color = "black") +
  geom_label(aes(label = labels), color = c("white", "white", "black", "white"),
            position = position_stack(vjust = 0.5),
            show.legend = FALSE) +
  guides(fill = guide_legend(title = "Answer")) +
  scale_fill_viridis_d() +
  coord_polar(theta = "y") + 
  theme_void()
```


## Popular Movie in Most popular genres

Following our question above, we decide to dive into the most popular genre "Drama" and see which movies get more rating in this genre. Some famous name come into view, "Shawshank Redemption", "Forrest Pump". Such movie is recommended all over world. I guess everyone who use movielen can't wait to see those classical film in the 90s!


```{r, echo = FALSE}

genres = rate %>% select(c("genres", "year", "rating", "title")) %>% 
   mutate(genres =  strsplit(genres,split='|', fixed=TRUE)) %>%
   unnest(c(genres))

genres_cnt = genres %>% group_by(genres) %>% 
  summarise(count = n(), mean_score = mean(rating)) %>%
  arrange(-count)

top_genre_data = genres_cnt[1, ]
top_genres =  c(top_genre_data$genres)

genres = genres %>% filter(genres %in% top_genres)

movie_cnt = genres  %>% group_by(title) %>% summarise(count = n(), mean_score = mean(rating))

movie_cnt = movie_cnt[order(movie_cnt$count, decreasing = TRUE),]

movie_cnt = movie_cnt[1:10, ]


ggplot(data=movie_cnt, aes(x=count, y=reorder(title, count))) +
    geom_bar(stat="identity") + 
  scale_y_discrete("Movie name", expand=c(0,0)) + 
  scale_x_continuous("Total Rate Count")
```


## Yearly Rating for The most popular Movie 

Then we look at the rating for the top 5 movies in drama genre. We compute average rating in each year for each movie, we find that some interesting facts:

* Forrest Gump and Braveheart got ratings in the beginning but these two movies suddenly got relatively low ratings in 1999. What happened?

* Forrest Gump get increasing rating trend from 2005 to 2019.

* While Pulp Fiction, Schindler's List and Shawshank Redemption got relatively high ratings from 1998 to 2004. These movies got a decreasing rating trend in next decade.And when it comes to braveheart, it get the worst trend among the five movies. It even got score lower than 3.8 in the 2018!

```{r, echo = FALSE,fig.width=8, fig.height=4}

genres = rate %>% select(c("genres", "year", "rating", "title")) %>% 
   mutate(genres =  strsplit(genres,split='|', fixed=TRUE)) %>%
   unnest(c(genres))

genres_cnt = genres %>% group_by(genres) %>% 
  summarise(count = n(), mean_score = mean(rating)) %>%
  arrange(-count)

top_genres = genres_cnt[1, ]
top_genre =  c(top_genres$genres)

genres = genres %>% filter(genres %in% top_genre)


movie_cnt = genres  %>% group_by(title) %>% summarise(count = n(), mean_score = mean(rating))

movie_cnt = movie_cnt[order(movie_cnt$count, decreasing = TRUE),]

movie_cnt = movie_cnt[1:5, ]

movie_trend = genres %>% filter(title %in% c(movie_cnt$title))


movie_year = movie_trend %>% group_by(year, title) %>% summarise(count = n(), mean_score = mean(rating))

movie_year = movie_year[order(movie_year$title, movie_year$year),]

ggplot(movie_year,) +
    geom_line( aes(year, mean_score, color = title, group = title)) + 
  theme_grey(10) +
  theme(legend.title = element_blank()) +
  scale_x_discrete(breaks = seq(1995, 2020, by = 3)) + 
  ylab("Average Rating[Out of]")

```

## Aluvial for famous movies


```{r, echo = FALSE,fig.width=8, fig.height=4}

movie_name = c("Forrest Gump (1994)", "Shawshank Redemption, The (1994)", 
  "Pulp Fiction (1994)" , "Schindler's List (1993)","Braveheart (1995)")

rate_f = rate %>% filter(title %in% movie_name)

```

